EGGs are adhesive!

### 2025-07-03 jlamp/finalArxiv.tex
JLAMP

\documentclass[a4paper,UKenglish,cleveref,pdftex,amsthm,thm-restate,numberwithinsect]{elsarticle}
\usepackage{stmaryrd}
\usepackage{bbding}
%\Envelope
\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}

@@

\title{EGGs are adhesive!}
%\titlerunning{EGGs are adhesive!} %TODO optional, please use if title is longer than one line

% Author with single affiliation.
\author[1]{Roberto Biondo}
\affiliation[1]{organization={Department of Computer Science, University of Pisa},
	addressline={},
	city={Pisa},
	citysep={},
	postcode={56127},
	state={},
	country={Italy}}
\ead{r.biondo@studenti.unipi.it}

\author[2]{Davide Castelnovo}
\ead{castelnovod@gmail.com}
\ead[url]{https://orcid.org/0000-0002-5926-5615}
\affiliation[2]{organization={Department of Computer Science, University of Pisa},
	addressline={},
	city={Pisa},
	citysep={},
	postcode={56127},
	state={},
	country={Italy}}

\author[3]{Fabio Gadducci}
\ead{fabio.gadducci@unipi.it}
\ead[url]{https://orcid.org/0000-0003-0690-3051}
\affiliation[3]{organization={Department of Computer Science, University of Pisa},
	addressline={},
	city={Pisa},
	citysep={},
	postcode={56127},
	state={},
	country={Italy}}

@@

>>>>

\documentclass[a4paper,UKenglish,cleveref,pdftex,amsthm,thm-restate,numberwithinsect]{cas-sc}
\usepackage{stmaryrd}
\usepackage{bbding}
%\Envelope
\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}

@@

\title[mode=title]{EGGs are adhesive!}
\tnotemark[1]

\tnotetext[1]{The research has been partially supported by the Italian MUR - Call PRIN 2022 - Project 20228KXFN2 ``Spatio-Temporal Enhancement of Neural nets for Deeply
Hierarchical Automatised Logic'' (STENDHAL) 
and by the University of Pisa - Call PRA 2022 - Project 2022\_99 ``Formal Methods for the Healthcare Domain based on Spatial Information'' (FM4HD).}

% Author with single affiliation.
\author[1]{Roberto Biondo}[type=editor]
\affiliation[1]{organization={Department of Computer Science, University of Pisa},
	city={Pisa},
%	citysep={},
	postcode={56127},
	country={Italy}}
\ead{r.biondo@studenti.unipi.it}

\author[1]{Davide Castelnovo}[type=editor,orcid=0000-0002-5926-5615]
\ead{castelnovod@gmail.com}
%\ead[url]{https://orcid.org/0000-0002-5926-5615}
%\affiliation[2]{organization={Department of Computer Science, University of Pisa},
%	addressline={},
%	city={Pisa},
%	citysep={},
%	postcode={56127},
%	state={},
%	country={Italy}}

\author[1]{Fabio Gadducci}[type=editor,orcid=0000-0003-0690-3051]
\cormark[1]
\fnmark[1]
\ead{fabio.gadducci@unipi.it}
%\ead[url]{https://orcid.org/0000-0003-0690-3051}
%\affiliation[3]{organization={Department of Computer Science, University of Pisa},
%       addressline={},
%       city={Pisa},
%       citysep={},
%       postcode={56127},
%       state={},
%       country={Italy}}

@@

\begin{keywords}
hypergraphs \sep terms graphs \sep e-graphs \sep adhesive categories
\end{keywords}
